Global Deaths Due to Air Pollution

### 2022-05-01 outline.Rmd
rearranged the percentage info to be in the beginning

@@

@@

# Reminder: Include this in the beginning 
First, we split the data into high and low population based on country

high_pop_countries

low_pop_countries

# Include Earlier to See who's been affected

@@

This shows us the deaths due to pollution, but what about the average population of those countries at that time?

```{r}
hp_countries_population <- world_pop %>% 
  filter(Country.Name %in% c('United States', 'Brazil', 'Nigeria', 'Germany', 'Pakistan', 'Australia'), Year > 1996) %>% 
  group_by(Country.Name) %>% 
  select(Count) %>% 
  summarize(average_population = mean(Count))

@@

>>>>

***
We selected a high population from each continent and used the formula below to determine the low population.

glimpse(high_pop_countries)

glimpse(low_pop_countries)
```

@@

*** 
So we've looked at the deaths due to pollution, but what percentage of the population was affected?

```{r, echo=FALSE, message=FALSE}
hp_countries_population <- world_pop %>% 
  filter(Country.Name %in% c('United States', 'Brazil', 'Nigeria', 'Germany', 'Pakistan', 'Australia'), Year > 1996) %>% 
  group_by(Country.Name) %>% 
  select(Count) %>% 
  summarize(average_population = mean(Count))

@@

# We have this included already

@@

@@

# Sources
